Parallel for Oregon Zip and WRF_Grid Intersection Proportion

### 2017-04-03 r_scripts/parallel_presentation.Rmd
Update parallel_presentation.Rmd
change some illustration

<ul class="incremental"> 
  <li> One choice: <br/>  simple calculation; copy and paste codes.</li> 
  <li> Another choice: for loop
  <br/> When analyzing big data set (for this data set, there are 417 zip codes 
  and 1610 WRF Grids in total), it is unrealistic to copy so many rows 
  (417*1610 = 671,370 times) of similar or same code.</li><br/>
  <li> And... <br/> Why using apply function? </li>
  <li> **Working Efficiency** <br/> **Vectorization.** Faster than for loop. It 
  works on margins of an array or matrix, not like for loop.</li> 
  <li> **Code Readability** <br/>  Understand the purporse more directly.</li> 
</ul>

@@

@@

@@

```{r parallel set, echo = FALSE}
# Setup for parallel computing before for loop ---------------------------------
cores <- detectCores() # 48
cl <- makeCluster(cores) # use half the cores on the vet cluster
registerDoParallel(cl)
# load packages on each cluster
clusterCall(cl, function() library(rgdal))
clusterCall(cl, function() library(sp))
clusterCall(cl, function() library(rgeos))

@@

```{r mcmapply, echo=FALSE}
start <- proc.time()

>>>>

<ul class="incremental"> 
  <li> One choice: <br/>  simple calculation; copy and paste codes.</li> 
  <li> Another choice: for loop
  <br/> When analyzing big data set (for this data set, there are 417 zip codes 
  and 1610 WRF Grids in total), it is unrealistic to copy so many rows 
  (417*1610 = 671,370 times) of similar or same code.</li><br/>
  <li> And... <br/> Why using apply function? </li>
  <li> **Working Efficiency** <br/> **Vectorization.** Faster than for loop. It 
  works on margins of an array or matrix, not like for loop.</li> 
</ul>

@@

An example: 
```{r, include = FALSE}
A <- matrix(1:4, 2, 2)
B <- matrix(5:10, 2, 3)
```

```{r}
L <- list(A, B)
lapply(L, "[", , 2)
```

@@

```{r}
L <- list(A, B)
sapply(L, function(x) x[ , 2])
```

@@

```{r parallel set, eval = FALSE}
# Setup for parallel computing before for loop ---------------------------------
cores <- detectCores() # 48
cl <- makeCluster(cores) # use half the cores on the vet cluster
registerDoParallel(cl)
# load packages on each cluster
clusterCall(cl, function() library(rgdal))
clusterCall(cl, function() library(sp))
clusterCall(cl, function() library(rgeos))

```{r parallel set, include = FALSE}
# Setup for parallel computing before for loop ---------------------------------
cores <- detectCores() # 48
cl <- makeCluster(cores) # use half the cores on the vet cluster
registerDoParallel(cl)
# load packages on each cluster
clusterCall(cl, function() library(rgdal))
clusterCall(cl, function() library(sp))
clusterCall(cl, function() library(rgeos))

@@

```{r mcmapply}
start <- proc.time()
